FTLR proof cases

### 2018-06-25 fully-abstract-comp/ftlr-proof-cases.tex
Avoid reproving the FTLR in the helper lemma.

\begin{lemma}
  \label{lem:ftlr-internal-lemma}
  If
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
  \item $\Phi_S(\pcreg) = \Phi_T(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$
  \item $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$
  \item $\memSat{\Phi_S.\mem,\Phi_S.\stk,\Phi_S.\ms_\stk,\Phi_T.\mem}{W_M}$
  \item $W_\pcreg \oplus W_R \oplus W_M$ is defined.
  \item Theorem~\ref{thm:ftlr} holds for all $n' < n$.
  \end{itemize}
  Then
  \[
    \npair{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  In the following we will use the following: $\reg_S = \Phi_S.\reg$, $\reg_T = \Phi_T.\reg$, $\ms_S = \Phi_S.\mem$, $\ms_\stk = \Phi_S.\ms_\stk$, and $\stk = \Phi_S.\stk$.

@@

    To this end let $W' \future \purePart{W_R}$ and $n' < n-1$ and $\aaddr' \in [\baddr',\eaddr']$ be given, and show
    \[
      \npair[n']{(((\rx,\normal),\baddr',\eaddr',\aaddr'),((\rx,\normal),\baddr',\eaddr',\aaddr'))} \in \lre(W')
    \]

    If $[\baddr',\eaddr'] = \emptyset$, then this is trivial, so assume $[\baddr',\eaddr'] \neq \emptyset$.
    Further, for $n'' \leq n'$ assume
    \begin{itemize}
    \item $\npair[n'']{\reg_S',\reg_T'} \in \lrr(W_R')$
    \item $\memSat{\ms_S',\stk',\ms_\stk',\ms_T'}{W_M'}$
    \item $W' \oplus W_R' \oplus W_M'$ is defined
    \end{itemize}
    and show
    \[
      \npair[n'']{\left(
          \begin{array}{l}
          (\ms_S',\reg_S'\update{\pcreg}{((\rx,\normal),\baddr',\eaddr',\aaddr')},\stk',\ms_\stk') \\
          (\ms_T',\reg_T'\update{\pcreg}{((\rx,\normal),\baddr',\eaddr',\aaddr')})
          \end{array}
         \right)} \in \lro
    \]
    To this end, we want to use the IH which means that we need the following:
    \begin{itemize}
    \item $\trust = \untrusted$ and $\npair[n'']{[\baddr',\eaddr']} \in \readCond{W'}$

      This follows from the readCondition assumption, Lemma~\ref{lem:conds-shrinkable}, Lemma~\ref{lem:downwards-closed}, Lemma~\ref{lem:monotonicity}, Lemma~\ref{lem:purePart-oplus}, and Lemma~\ref{lem:non-linear-pure}.
    \item $\npair[n'']{[\baddr',\eaddr']} \in \xReadCond{W'}$

      This follows from what we already showed about the readXCondition,
      Lemma~\ref{lem:conds-shrinkable}, Lemma~\ref{lem:downwards-closed}, and Lemma~\ref{lem:monotonicity}
    \item $\npair[n'']{\reg_S',\reg_T'} \in \lrr(W_R')$

      By assumption.
    \item $\memSat{\ms_S',\stk',\ms_\stk',\ms_T'}{W_M'}$

      By assumption.

    \item $W' \oplus W_R' \oplus W_M'$ is defined

      By assumption
    \end{itemize}
  \end{itemize}

>>>>

\begin{lemma}
  \label{lem:ftlr-internal-lemma}
  If
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $[b,e] \mathrel{\#} \ta$ and $\npair{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
  \item $\Phi_S(\pcreg) = \Phi_T(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$
  \item $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$
  \item $\memSat{\Phi_S.\mem,\Phi_S.\stk,\Phi_S.\ms_\stk,\Phi_T.\mem}{W_M}$
  \item $W_\pcreg \oplus W_R \oplus W_M$ is defined.
  \item Theorem~\ref{thm:ftlr} holds for all $n' < n$.
  \end{itemize}
  Then
  \[
    \npair{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  In the following we will use the following: $\reg_S = \Phi_S.\reg$, $\reg_T = \Phi_T.\reg$, $\ms_S = \Phi_S.\mem$, $\ms_\stk = \Phi_S.\ms_\stk$, and $\stk = \Phi_S.\stk$.

@@

    To this end let $W' \future \purePart{W_R}$ and $n' < n-1$ and $\aaddr' \in [\baddr',\eaddr']$ be given, and show
    \[
      \npair[n']{(((\rx,\normal),\baddr',\eaddr',\aaddr'),((\rx,\normal),\baddr',\eaddr',\aaddr'))} \in \lre(W')
    \]
    This follows immediately from the FTLR: we know that $[b,e] \mathrel{\#} \ta$ since $\trust = \untrusted$ and we know that $n' < n - 1 < n$.
  \end{itemize}
